### 2021-03-12 text/text.tex
add conclusion

In a first step, the keywords must be extracted from the Edoc sample
data set \texttt{/sample/sample\_master.json}. Recall that we mandated a
non-empty \texttt{keywords} data field for an item to be selected from
the raw Edoc data (see \protect\hyperlink{selection}{subsection
``Selection''}). We can thus simply copy the information in the
\texttt{keywords} data field on a per item basis. To do this, we call
\texttt{Keywords.extract\_keywords} with the sample data set as argument
and save the output as \texttt{keywords/keywords\_extracted.json} like
so:

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{keywords\_extracted }\OperatorTok{=}\NormalTok{ Utility.load\_json(}\StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ Keywords.clean\_keywords(keywords\_extracted)}
\NormalTok{Utility.save\_json(keywords\_clean, }\StringTok{"keywords/keywords\_clean.json"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ Utility.load\_json(}\StringTok{"/keywords/keywords\_clean.json"}\NormalTok{)}
\NormalTok{keywords\_histogram }\OperatorTok{=}\NormalTok{ Keywords.make\_histogram(keywords\_clean)}
\NormalTok{Utility.save\_json(keywords\_histogram, }\StringTok{"keywords/keywords\_clean\_histogram.json"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{figure}
\centering
\includegraphics{images/keywords_clean_histogram_abc.pdf}
\caption{In \texttt{keywords/keywords\_clean\_histogram.json}, the
distribution of keywords is strongly skewed right (min = Q1 = M = Q3 =
1, max = 910). However, even though keywords with only one occurrence
constitute over 75\% of the total keywords, their occurrences constitute
less than 35\% of the total occurrences. The most common keywords with
50 or more occurrences are extreme outliers but make up almost 20\% of
the total occurrences.}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{keywords\_reference }\OperatorTok{=}\NormalTok{ Utility.load\_json(}\StringTok{"/keywords/keywords\_reference.json"}\NormalTok{)}
\NormalTok{keywords\_reference\_new }\OperatorTok{=}\NormalTok{ Keywords.enrich\_with\_yso(keywords\_reference)}
\NormalTok{Utility.save\_json(keywords\_histogram, }\StringTok{"keywords/keywords\_reference\_master.json"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

In this section I will assess the quality of the sample data set's
indexing by Annif based on the gold standard.

@@

The main take home from this project is that the out of the box Annif
API is suitable to index an institutional repository such as Edoc.

!! improve data collection of keywords

!! Answer some questions asked in the proposal. Briefly summarize
results. Recommend using Out of the box annif for production. sketch
implementation strategy.

Apart from implementing a production system as discussed above, natural
next steps to build on this project include:

@@

@@

>>>>

In a first step, the keywords must be extracted from the Edoc sample
data set \texttt{/sample/sample\_master.json}. Recall that we mandated a
non-empty \texttt{keywords} data field for an item to be selected from
the raw Edoc data (see \protect\hyperlink{selection}{subsection
``Selection''}). We can thus simply copy the information in the
\texttt{keywords} data field on a per item basis. To do this, we call
\texttt{Keywords.extract\_keywords} with the sample data set as argument
and save the output as \texttt{/keywords/keywords\_extracted.json} like
so:

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{keywords\_extracted }\OperatorTok{=}\NormalTok{ Utility.load\_json(}\StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ Keywords.clean\_keywords(keywords\_extracted)}
\NormalTok{Utility.save\_json(keywords\_clean, }\StringTok{"/keywords/keywords\_clean.json"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ Utility.load\_json(}\StringTok{"/keywords/keywords\_clean.json"}\NormalTok{)}
\NormalTok{keywords\_histogram }\OperatorTok{=}\NormalTok{ Keywords.make\_histogram(keywords\_clean)}
\NormalTok{Utility.save\_json(keywords\_histogram, }\StringTok{"/keywords/keywords\_clean\_histogram.json"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{figure}
\centering
\includegraphics{images/keywords_clean_histogram_abc.pdf}
\caption{In \texttt{/keywords/keywords\_clean\_histogram.json}, the
distribution of keywords is strongly skewed right (min = Q1 = M = Q3 =
1, max = 910). However, even though keywords with only one occurrence
constitute over 75\% of the total keywords, their occurrences constitute
less than 35\% of the total occurrences. The most common keywords with
50 or more occurrences are extreme outliers but make up almost 20\% of
the total occurrences.}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{keywords\_reference }\OperatorTok{=}\NormalTok{ Utility.load\_json(}\StringTok{"/keywords/keywords\_reference.json"}\NormalTok{)}
\NormalTok{keywords\_reference\_new }\OperatorTok{=}\NormalTok{ Keywords.enrich\_with\_yso(keywords\_reference)}
\NormalTok{Utility.save\_json(keywords\_histogram, }\StringTok{"/keywords/keywords\_reference\_master.json"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

In this section I will assess the quality of the sample data set's
indexing by Annif based on the derivative gold standard.

@@

The main take home from this project is that the out of the box Annif
API is suitable to index an institutional repository such as Edoc. This
is based on the performance of the Annif API in indexing the Edoc sample
data set measured against the derivative gold standard constructed from
cleaned and reconciled Edoc author keywords. With the prototype in
place, the next step now concerns the implementation of a production
system. The function \texttt{Data.enrich\_with\_annif} can of course be
called to index all Edoc data available at \texttt{/raw/}. It would also
be relatively straightforward to implement indexing with Annif for items
newly added to Edoc respectively the University of Basel's research
database. An alternative and perhaps more sustainable approach would be
to improve the data quality by amending the process and requirements for
data entry. Generally speaking, authors should be required to choose
index terms from a controlled vocabulary or from a set of controlled
vocabularies, and the entered data should be automatically validated.
One way to implement this would be via the Skosmos recommendations
feature of the BARTOC Skomos instance (see Waeber and Ledl 2019).

Apart from implementing a production system as discussed above, natural
next steps to improve upon this project include:

@@

Finally, I had initially {[}monitoring,,,{]}.

@@

\leavevmode\hypertarget{ref-Waeber.2019}{}%
Waeber, Jonas, and Andreas Ledl. 2019. {``A Semantic Web SKOS Vocabulary
Service for Open Knowledge Organization Systems.''} In \emph{Metadata
and Semantic Research}, edited by Emmanouel Garoufallou, Fabio Sartori,
Rania Siatri, and Marios Zervas, 846:3--12. Communications in Computer
and Information Science, 1865-0929. Cham, Switzerland: Springer.
\url{https://doi.org/10.1007/978-3-030-14401-2\%7B/textunderscore\%20\%7D1}.

### 2021-03-12 text/titlepage/titlepage.tex
add conclusion

\newpage
%\sffamily
\thispagestyle{empty}
\large
\begin{center}
	\includegraphics[width=5cm]{./logo.png}\\[.5cm]
	Universität Zürich, Philosophische Fakultät\\[.25cm]
 	Zentralbibliothek Zürich, MAS Bibliotheks- und Informationswissenschaft\\[1cm]
	\hrule
	\vspace{2cm}
	\flushleft
	\textbf{\LARGE Machine indexing of institutional repositories: indexing Edoc with Annif as proof of concept}\\[2cm]
	\orcidicon{0000-0002-9337-4655} Dr.\ Maximilian G.\ Hindermann\\
	Spalentorweg 46, CH-4051 Basel\\
	+41 79 277 0612\\
	\href{mailto:maximilian.hindermann@gmail.com}{maximilian.hindermann@gmail.com}\\
	\vspace{1cm}
	\flushleft
	\orcidicon{0000-0003-1952-1933} Silke Bellanger, Referentin\\[.25cm]
	\orcidicon{0000-0002-0629-0446} Dr.\ Andreas Ledl, Ko-Referent\\
	%Prof.\ Marco J.\ Nathan\\[.25cm]
	%\begin{minipage}{.4\textwidth}
	%\end{minipage}
	\vfill
	\center
	1.\ April 2021
\end{center}
\normalfont
\normalsize

>>>>

\newpage
%\sffamily
\thispagestyle{empty}
\large
\begin{center}
	\includegraphics[width=5cm]{./logo.png}\\[.5cm]
	Universität Zürich, Philosophische Fakultät\\[.25cm]
 	Zentralbibliothek Zürich, MAS Bibliotheks- und Informationswissenschaft\\[1cm]
	\hrule
	\vspace{2cm}
	\flushleft
	\textbf{\LARGE Machine indexing of institutional repositories: indexing Edoc with Annif as proof of concept}\\[2cm]
	Dr.\ Maximilian G.\ Hindermann \orcidicon{0000-0002-9337-4655}\\
	Spalentorweg 46, CH-4051 Basel\\
	+41 79 277 0612\\
	\href{mailto:maximilian.hindermann@gmail.com}{maximilian.hindermann@gmail.com}\\
	\vspace{1cm}
	\flushleft
	Silke Bellanger, Referentin \orcidicon{0000-0003-1952-1933}\\[.25cm]
	Dr.\ Andreas Ledl, Ko-Referent \orcidicon{0000-0002-0629-0446}\\
	%Prof.\ Marco J.\ Nathan\\[.25cm]
	%\begin{minipage}{.4\textwidth}
	%\end{minipage}
	\vfill
	\center
	1.\ April 2021
\end{center}
\normalfont
\normalsize
